---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
#Course Reproducible Research - R Markdown project 

##1) Code for reading in the dataset and/or processing the data
```{r}
library(dplyr)
library(ggplot2)
setwd("~/MEGAsync/DATA-SCIENCE/work/c5-w2-project")
activity <- read.csv("activity.csv")
activitydt<-tbl_df(activity)
```


##2) Histogram of the total number of steps taken each day
```{r}
stepbydate<-activitydt %>% group_by(date) %>% summarise(totalbyday=sum(steps,na.rm = TRUE)) 
stepbydate$date<-as.Date(stepbydate$date,"%Y-%m-%d")
ggplot(data = stepbydate, aes(date, totalbyday))+stat_summary(fun.y = sum,geom = "bar") +xlab("Day") + ylab("Total steps by day")
```

##3) Mean and median number of steps taken each day

```{r}
meanstepbydate<-activitydt %>% group_by(interval) %>% summarise(mean=mean(steps,na.rm=TRUE))
medianstepbydate<-activitydt %>% group_by(interval) %>% summarise(median=median(steps,na.rm=TRUE))
cbind(meanstepbydate, median=medianstepbydate$median)
mean(stepbydate$totalbyday)
median(stepbydate$totalbyday)
```

##4) Time series plot of the average number of steps taken

```{r}
stepbyinterval <- activitydt %>% group_by(interval) %>% summarise(avgbyinterval=mean(steps,na.rm=TRUE))
plot(stepbyinterval$interval,stepbyinterval$avgbyinterval,type="l", main="Average number of steps taken", xlab="5 minute interval", ylab="Average steps")
```

##5) The 5-minute interval that, on average, contains the maximum number of steps
```{r}
filter(stepbyinterval, avgbyinterval==max(stepbyinterval$avgbyinterval))
```

##6)Code to describe and show a strategy for imputing missing data

The mean of the interval in assigned for NA measures
```{r}
for (i in 1:nrow(activitydt)) {
    rowact <- activitydt[i,]
    meaninterval<-filter(stepbyinterval,interval==rowact$interval) 
    if(is.na(activitydt[i,]$steps)) {
      activitydt[i,]$steps<-meaninterval$avgbyinterval
    }
}
```

##7) Histogram of the total number of steps taken each day after missing values are imputed

```{r}
stepbydate2<-activitydt %>% group_by(date) %>% summarise(totalbyday=sum(steps)) 
stepbydate2$date<-as.Date(stepbydate2$date,"%Y-%m-%d")
ggplot(data = stepbydate2, aes(date, totalbyday))+stat_summary(fun.y = sum,geom = "bar") +xlab("Day") + ylab("Total steps by day after NA cleaning")
```

Mean and Median after removing NA value have increased
```{r}
mean(stepbydate2$totalbyday)
median(stepbydate2$totalbyday)
```

##8) Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
library(chron)
activitydt$date<-as.Date(activitydt$date,"%Y-%m-%d")
activitydt <-mutate(activitydt,wend=is.weekend(activitydt$date))
activitydtnowend <-filter(activitydt,!wend)
activitydtwend <-filter(activitydt,wend)
stepbyintervalnowend <- activitydtnowend %>% group_by(interval) %>% summarise(avgbyinterval=mean(steps,na.rm=TRUE))
stepbyintervalwend <- activitydtwend %>% group_by(interval) %>% summarise(avgbyinterval=mean(steps,na.rm=TRUE))
par(mfrow=c(1,2))
plot(stepbyintervalnowend$interval,stepbyintervalnowend$avgbyinterval,type="l", main="Average steps in workdays", xlab="5 minute interval", ylab="Average steps")
plot(stepbyintervalwend$interval,stepbyintervalwend$avgbyinterval,type="l", main="Average steps taken in weekend", xlab="5 minute interval", ylab="Average steps")
```
